%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {\href{https://github.com/matl1995/DAI}{Github link}} % Project URL
  {Restaurant management website} % Project title
  {Django y Bootstrap} % Project programming language
  {Sep. 2017 - Jan. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Final project for the subject \textbf{Web applications developement}.}
      \item {Web developed with \textbf{Django} and user interface with \textbf{Bootstrap}.}
      \item {Simplified management of restaurants located in a \textbf{MongoDB} data base.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {\href{https://github.com/matl1995/PW}{Github link}} % Project URL
  {DEC - Social media website} % Project title
  {HTML, CSS, PHP, JS y MySQL} % Project programming language
  {Feb. 2017 - Jun. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Final project for the subject \textbf{Web programming}.}
      \item {Web based on the classic functionality of a social media application.}
      \item {Allows users to sign up, post content and comment on posts.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/matl1995/TFG}{Github link}} % Project URL
    {Augmented board game using ARCore} % Project title
    {Android, Unity, ARCore} % Project programming language
    {Sep. 2017 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research and developement project about \textbf{Augmented Reality} technologies using \textbf{Unity} engine.}
        \item {Focused on the \textbf{ARCore} platform.}
        \item {Planning and development carried out using \textbf{agile development methodologies}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/matl1995/PDM/tree/master/Museo}{Github link}} % Project URL
    {Interactive museum via QR code} % Project title
    {Android} % Project programming language
    {Feb. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Final project for the subject \textbf{Application programming for mobile devices}.}
        \item {Android application using \textbf{QR} code scanning.}
        \item {When reading the code of a work of art from a museum, it presents a related quiz to the user.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
