%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {{In development}} % Project URL
    {AR game with ARCore API} % Project title
    {Android, Unity, ARCore} % Project programming language
    {Sep. 2017 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research and developement project about \textbf{Augmented Reality} technologies using \textbf{Unity} framework.}
        \item {Focused on \textbf{ARCore} platform.}
        \item {Mobile application with \textbf{educational} purposes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/matl1995/DAI}{Github link}} % Project URL
    {Restaurant management website} % Project title
    {Django y Bootstrap} % Project programming language
    {Sep. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Final project for \textbf{Internet application developement} subject.}
        \item {Web developed with \textbf{Django} and user interface with \textbf{Bootstrap}.}
        \item {Simplified management of restaurants located in a \textbf{MongoDB} data base.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/matl1995/PW}{Github link}} % Project URL
    {DEC - Social medium} % Project title
    {HTML, CSS, PHP, JS y MySQL} % Project programming language
    {Feb. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Final project for \textbf{Web programming} subject.}
        \item {Web based on the functionality of social media.}
        \item {Allows users to sign up, post content and comment on posts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/matl1995/PDM/tree/master/Museo}{Github link}} % Project URL
    {Interactive museum via QR code} % Project title
    {Android} % Project programming language
    {Feb. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Final project for \textbf{Application programming for mobile devices} subject.}
        \item {Android application using \textbf{QR} code scanning.}
        \item {When reading the code of a work of art from a museum, it presents the user a quiz related to it.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
